Machine Learning Approach to Soccer Player's Overall Rating Prediction

### 2021-12-11 Paper/main.tex
Update main.tex

\subsection{Dateset overall}

@@

\subsection{Data processing}

@@

\section*{Solution}
\subsection*{Feature Engineering}
The process of taking raw data and extracting or creating new features that allow a machine learning model to learn a mapping between these features and the target. This might mean taking transformations of variables, such as we did with the log and square root, or one-hot encoding categorical variables so they can be used in a model. Generally, we think of feature engineering as adding additional features derived from the raw data.
In this project, we take the following steps:
\begin{itemize}
    \item Group similar data(delete positions rating)
    \item Convert object type variables to numerical by label encoding(transform string type to int type)
\end{itemize}

@@

>>>>

\subsection*{Dateset overall}

@@

\subsection*{Data processing}

@@

\section*{Solution}
We implement 5 models \textbf{Linear Regression}, \textbf{Random Forest}, \textbf{Gradient Boosted}, \textbf{K-Nearest Neighbors} and \textbf{Neural Network}. Below, we will introduce our workflow.

\subsection*{Feature Engineering}
The process of taking raw data and extracting or creating new features that allow a machine learning model to learn a mapping between these features and the target. This might mean taking transformations of variables, such as we did with the log and square root, or one-hot encoding categorical variables so they can be used in a model. Generally, we think of feature engineering as adding additional features derived from the raw data.
In this project, we take the following steps:
\begin{itemize}
    \item Group similar data(delete positions rating)
    \item Convert object type variables to numerical by label encoding(transform string type to int type)
\end{itemize}

@@

\subsection*{Model}.
We will compare five different machine learning models using the great Scikit-Learn library:
\begin{itemize}
    \item Linear Regression
    \item Random Forest Regression
    \item Gradient Boosting Regression
    \item K-Nearest Neighbors Regression
    \item Neutral Network
\end{itemize}

To compare the models, we are going to be mostly using the Scikit-Learn defaults for the model hyperparameters. Generally these will perform decently, but should be optimized before actually using a model. At first, we just want to determine the baseline performance of each model, and then we can select the best performing model for further optimization using hyperparameter tuning. The default hyperparameters will get a model up and running, but nearly always should be adjusted using some sort of search to find the best settings for your problem!

\subsection*{Metric:}
\subsubsection*{Root Mean Square Error}
Root Mean Square Error (RMSE) is the standard deviation of the residuals (prediction errors). Residuals are a measure of how far from the regression line data points are; RMSE is a measure of how spread out these residuals are. In other words, it tells you how concentrated the data is around the line of best fit. Root mean square error is commonly used in climatology, forecasting, and regression analysis to verify experimental results.

\subsubsection*{$R^2$ Score}
The $R^2score$ function computes the coefficient of determination. It represents the proportion of variance (of y) that has been explained by the independent variables in the model. It provides an indication of goodness of fit and therefore a measure of how well unseen samples are likely to be predicted by the model, through the proportion of explained variance.

\begin{center}
\includegraphics[scale=0.5]{rmse.png}\\
\caption{Image 1, Model Comparison on RMSE}\\
\includegraphics[scale=0.5]{r2score.png} \\
\caption{Image 2, Model Comparison on $R^2$ Score}
\end{center}

Depending on the run (the exact results change slighty each time), the Neutral Network performs the best. We have to admit that this is not the most fair comparison because we are using mostly the default hyperparameters. Nonetheless, from these results, we can conclude that machine learning is applicable because all the models significantly outperform the baseline!
From here, We are going to concentrate on optimizing the best model using hyperparamter tuning. Given the results here, we will concentrate on using the Linear Regression and  Neutral Network.

\subsection*{Model Optimization}
In machine learning, optimizing a model means finding the best set of hyperparameters for a particular problem.

\subsubsection*{Hyperparameters}
First of all, we need to understand what model hyperparameters are in contrast to model parameters :

Model hyperparameters are best thought of as settings for a machine learning algorithm that are tuned by the data scientist before training. Examples would be the number of trees in the random forest, or the number of neighbors used in K Nearest Neighbors Regression.
Model parameters are what the model learns during training, such as the weights in the linear regression. We as data scientists control a model by choosing the hyperparameters, and these choices can have a significant effect on the final performance of the model (although usually not as great of an effect as getting more data or engineering features). Tuning the model hyperparameters controls the balance of under vs over fitting in a model. We can try to correct for under-fitting by making a more complex model, such as using more trees in a random forest or more layers in a deep neural network. A model that underfits has high bias, and occurs when our model does not have enough capacity (degrees of freedom) to learn the relationship between the features and the target. We can try to correct for overfitting by limiting the complexity of the model and applying regularization. This might mean decreasing the degree of a polynomial regression, or adding dropout layers to a deep neural network. A model that overfits has high variance and in effect has memorized the training set. Both underfitting and overfitting lead to poor generalization performance on the test set.
The problem with choosing the hyperparameters is that no set will work best across all problems. Therefore, for every new dataset, we have to find the best settings. This can be a time-consuming process, but luckily there are several options for performing this procedure in Scikit-Learn.

\subsection*{Evaluate Final Model on the Test Set}
